Lattices of acyclic pipe dreams

### 2023-01-31 acyclicFacets/draft/latticePipeDreams.tex
Nantel: small typo in Fig 1

\begin{figure}[t]
	\centerline{
		%\input{pipeDreams}
		\includegraphics[scale=.9]{pipeDreams}
	}
	\caption{Two pipe dreams of~$\pipeDreams(1365724)$ connected by an increasing flip (exchanging a contact with the crossing on the two red pipes~$3$ and~$4$).}
	\label{fig:pipeDreams}
\end{figure}

>>>>

\begin{figure}[t]
	\centerline{
		%\input{pipeDreams}
		\includegraphics[scale=.9]{pipeDreams}
	}
	\caption{Two pipe dreams of~$\pipeDreams(1365724)$ connected by an increasing flip (exchanging a contact with the crossing on the two red pipes~$4$ and~$5$).}
	\label{fig:pipeDreams}
\end{figure}
